---
title: "EDA Capstone"
subtitle: "Capstone 2021: Exploratory Time Series Forecasting"
author:
- "Willem van der Schans"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document:
    fig_height: 4
    fig_width: 8
    highlight: kate
    toc: no
    toc_depth: 4
    number_sections: true
header-includes:
  - \usepackage{longtable}
---

\newpage\null\thispagestyle{empty}\newpage

\tableofcontents


\newpage\null\thispagestyle{empty}\newpage


```{r, include=FALSE}
library(dplyr) # Additional Base level functionality of R 
library(stats) # Base Statistic Funtionality

# Extended Base Functionality
library(reshape2) # Melt Function Correlation Matrix
library(rlist) #list.append
library(lubridate) # For working with dates
library(caret) # MachineLearning package used for createDataPartition

# Visualisation Packages
library(ggplot2) # Comprehensive Graphical Output Package 
library(ggthemes) # More themes for GGPLOT2
library(scales) # Control over Axis formatting
library(gghighlight) # GGplot Highlight function
library(gridExtra) # Plot in Grids

# Latex Packages
library(xtable) # Latex Tables
library(papeR) # Paper Writing Module
library(reporttools) # Latex Sumarry Tables
```


# Data Set-up

```{r}
download.file(
  "https://github.com/Kydoimos97/CapstoneMSBA2020/raw/main/Data/CapstoneProjectInfoRevised.rds", 
  destfile = "CapstoneProjectInfoRevised.rds")

download.file(
  "https://github.com/Kydoimos97/CapstoneMSBA2020/raw/main/Data/CapstoneProjectProducts.rds", 
  destfile= "CapstoneProjectProducts.rds")

df <- readRDS("CapstoneProjectInfoRevised.rds")
products <- readRDS("CapstoneProjectProducts.rds")
```

## Setting Data Types

```{r}
# Factorization
df$Site_ID <- as.factor(df$Site_ID)
df$Location_ID <- as.factor(df$Location_ID)
df$Locale <- as.factor(df$Locale)
df$Fiscal_Period <- as.factor(df$Fiscal_Period)
df$MPDS <- as.factor(df$MPDS)
df$Project <- as.factor(df$Project)

# Numeration
df$Quantity_Sold <- as.numeric(df$Quantity_Sold)
df$SQ_Footage <- as.numeric(df$SQ_Footage)# Shows Factor like tendencies
df$Periodic_GBV <- as.numeric(df$Periodic_GBV)
df$Current_GBV <- as.numeric(df$Current_GBV)

# Re-origin of Dates at 06/22/1998

x <- min(df$Open_Date) 
df$Open_Date <- as_date(df$Open_Date, origin = x)
df$DATE <- as_date(df$DATE, origin = x)

rm(x)

# enables DATE to be used in prediction algorithms

```

A Date format in R is based on epoch time and thus easily convert to a number. The origin is reset to the earliest date present in the data set. Setting the origin allows us to work with an origin point that holds value [06/22/1998] instead of the arbitrary origin point of epoch [1/1/1970]

```{r, warning=FALSE, message=FALSE}
candy_vector <- c(products$Item_Desc)

id_vector <- c(products$Item_ID)

df$Item_desc <- df$Item_ID
df$Item_desc <- plyr::mapvalues(df$Item_desc, id_vector, candy_vector)

df$Item_ID <- as.factor(df$Item_ID)

# Reodering Data
df <- df[, c(1,2,6,17,7,3,12,13,14,10,11,8,9,15,16,4,5)]

#Rename Variables
names(df) <- tolower(make.names(names(df)))

rm(products, candy_vector, id_vector)

```

\newpage


### Removal and Creation of variables

```{r}
# creation of tempdiff
df$temp_diff <- as.numeric(df$maxtemp-df$mintemp)

# Creation of cgbv_sqf
df$cgbv_sqf <- as.numeric(df$current_gbv/df$sq_footage)

# creation of diff_gbv
df$diff_gbv <- df$current_gbv - df$periodic_gbv

#Days open
x <- min(df$open_date) 
df$days_open <- as.numeric(df$date-df$open_date)

rm(x)

df <- df[, c(1,2,3,4,21,6,7,19,20,10,18,12,13,14,15,16,17,8,9,11,5)]

df <- df[,-c(12,18,19,20,21)]
```


# Time Series Model

## Reshape Data Set

```{r}
sum_sales <- aggregate(ifelse(df$sales > 150, 150, df$sales)
                       , by=list(df$date, df$site_id), FUN=sum)
names(sum_sales) <- c("date", "site_id", "sum_of_sales")

sum_sales <- dcast(sum_sales, date ~ site_id, value.var ="sum_of_sales")
sum_sales <- sum_sales[-c(2,9,10,11)]

daysdifference <- min(sum_sales$date) - as.Date("2017/01/01", format = "%Y/%m/%d")
maxdate <- max(sum_sales$date)

train <- subset(sum_sales, date <=  maxdate  - 10)[-1]
  
test <- subset(sum_sales, date >  maxdate  - 10)
datelist <- test$date
test <- test[-1]

mymts = ts(train,
           frequency = 365,
           start = c(2017, daysdifference))
```

# Dickey Fuller Test

```{r}
apply(mymts, 2, tseries::adf.test)
```

## Stationary Time Series

```{r}
stnry <- MTS::diffM(mymts)

plot.ts(stnry)
apply(stnry, 2, tseries::adf.test)
```

## Variable Selection

```{r}
vars::VARselect(stnry, 
          type = "none", #type of deterministic regressors to include. We use none becasue the time series was made stationary using differencing above. 
          lag.max = 10) #highest lag order
```

## Time Series Regression


```{r}
# Creating a VAR model with vars
var.a <- vars::VAR(stnry,
                   lag.max = 25, #highest lag order for lag length selection according to the choosen ic
                   ic = "AIC", #information criterion
                   type = "none") #type of deterministic regressors to include
summary(var.a)


```

## Serial Test

```{r}
vars::serial.test(var.a)
```

## Creating and preparing Predictions

```{r}
# selecting the variables
# Granger test for causality
 
vars::causality(var.a, #VAR model
          cause = c("X380"))

fcast = predict(var.a, n.ahead = 10)
par(mar = c(2.5,2.5,2.5,2.5))

X380 = fcast$fcst[1]; X380 
x = X380$X380[,1]; x

tail(mymts)


x = cumsum(x) + 733.10
par(mar = c(2.5,2.5,1,2.5)) #bottom, left, top, and right

test380 <- test$`380`
diff = test380-x

result <- data.frame(test = c(test380), 
                     difference = c(diff), 
                     prediction =  c(x), 
                     date = datelist)


result %>% ggplot(aes(x = date, y = prediction)) +
  geom_line() + geom_line(aes(y=test), color="red") + theme_bw() +
  ggtitle(paste0("Relationship of sales and ", "380", sep= " ")) +  
  theme(legend.position="right",legend.direction = "vertical", legend.text = element_text(size=7))

test[,1]
```

## Calculate Mean Difference

```{r, fig.height = 9, fig.width = 7, warning=FALSE, message=FALSE}
listsites <- c(380,399, 459, 516, 517, 554)
counter = 0
plot_list <- list(1)
g <- NULL
result <- NULL

for (i in listsites) {
  g <- NULL
  result <- NULL
  counter = counter+1
  x = fcast$fcst[counter]
  x = as.data.frame(x)
  x = unlist(x[1])
  p = as.numeric(tail(mymts,2)[2,counter])
  x =  cumsum(x) + p
  par(mar = c(2.5,2.5,1,2.5))
  
  g <- test[,counter]
  diff = g-x
  
  result <- data.frame(test = g, 
                     difference = diff, 
                     prediction =  x, 
                     date = datelist)
                     
  o = ggplot(data=result, aes_string(x = "date", y="prediction")) +
      geom_line() + geom_line(aes_string(y="test"), color="red") + geom_line(aes_string(y="diff"), color = "Grey") +
      theme_fivethirtyeight() + ggtitle(paste0("Site = ", as.character(i), sep= " ")) + theme(plot.title = element_text(size=10)) 

  assign(paste0("plt", i), o)
  plot_list <- rlist::list.append(plot_list, o)
  
  print(paste0("mean error for ",i, " = ", mean(diff)))

}
```

## Plot Results

```{r, fig.height = 9, fig.width = 7, fig.cap='Predictions of Time Series', warning=FALSE, message=FALSE}
plot_list <- plot_list[-1]

nCol <- floor(sqrt(length(plot_list)))

grid.arrange(grobs=plot_list, widths = c(1,1), ncol=2, layout_matrix =  rbind(c(1,2),
                                                                                 c(3,4), 
                                                                                 c(5,6)), 
             top = "Predicted time series")


```





